Path Model Temperature Comparisons

### 2016-07-13 path-temp-compare.Rmd
Add chunk that combines data for all plots.

>>>>

```{r combine plots data, eval=F, echo=F}
soco_plots <- stems %>%
      select(plotid, species, year) %>%
      group_by(plotid, year) %>%
      # filter(species == "UMCA", status == "Alive") %>%
      summarise(stem_total = length(species))

soco_plots <- rename(soco_plots, sample_year = year)

soco_plots <- left_join(soco_plots, select(umca_plots, plotid:tot_lfct), by = c("plotid", "sample_year"))
soco_plots <- left_join(soco_plots, select(oakplots.sub, plotid:inf_oak_ct), by = c("plotid","sample_year"))
soco_plots <- left_join(soco_plots, plots_env, by = "plotid")
summary(soco_plots)
soco_plots <- select(soco_plots, -stem_total)

write.csv(soco_plots, "analysis/data/soco_plots.csv")
```
